---
title: "ReviewerTools: Quick Start"
name: Marcel Ramos
date: "Compiled `r BiocStyle::doc_date()`; Modified 14 February 2025"
vignette: |
  %\VignetteIndexEntry{ReviewerTools: Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    toc_float: true
package: ReviewerTools
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

# ReviewerTools

The goal of `ReviewerTools` is to provide a set of tools to facilitate the
review process of R / Bioconductor packages. The package is designed to
use a mix of R packages and `system` commands to clone, install, build, and
check packages from the Bioconductor GitHub contributions repository.

## Installation

You can install the development version of `ReviewerTools` from GitHub with:

```{r,eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("Bioconductor/ReviewerTools")
```

## Setup

In order to use the `gh` package, you will need to create a GitHub personal
access token. You can do this by going to your GitHub account settings, then
clicking on "Developer settings" -> "Personal access tokens" -> "Fine-grained
Tokens". You will need to select either "All repositories" or "Only select
repositories" under "Repository Access." You can then add the token using:

```{r,eval=FALSE}
library(gitcreds)
gitcreds_set()
```

### Using Bioconductor Docker

We highly recommend using the Bioconductor Docker containers to run the
`ReviewerTools` package. Refer to the
[Bioconductor Docker](https://bioconductor.org/help/docker/) page for more
information. We also recommend using our convenience script to run the
Bioconductor Docker container with the volume mounts for installed packages. See
the GitHub repository <https://github.com/waldronlab/bioconductor/>. Using
the script, one can run the Bioconductor Docker container with the following:

```sh
./bioconductor -v devel 
```

Note that the `ReviewerTools` package must be installed separately within the
container.

## Usage

### Package load

```{r}
library(ReviewerTools)
```

### Install, build, and check on GitHub issues

The main function in `ReviewerTools` is `check_github_issues`, which pulls
all the reviewer's issues from the `Bioconductor/contributions` repository
and checks the associated packages. In order to obtain the issues, the
`gh` package is used to interact with the GitHub API. The function to
retrieve the issues is `get_assigned_packages`.

```{r}
reviews <- get_assigned_packages("LiNk-NY")
class(reviews)
```

The `check_github_issues` function processes a list of GitHub issues, cloning
the repositories, installing dependencies, building the package, and checking
the package. In this example, we will run `check_github_issues` on the first
assigned review by subsetting the `reviews` object with a single bracket `[`
subset.

```{r}
dir.create(tdr <- tempfile())
check_github_issues(reviews[1L], base_repo_dir = tdr, output_dir = tdr)
```

## Inspecting outputs

The `check_github_issues` function will clone the packages in the
`base_repo_dir` and save any outputs to the `output_dir`. For flexibility,
the folder location may be different. One can inspect the outputs with a
text editor or with R via:

```{r}
pkgName <- basename(list_assigned_issues(reviews[1L]))
inst_file <- file.path(tdr, paste0(pkgName, "_install.txt"))
readLines(inst_file)
```

## Session Info

<details> <summary> Click here to expand </summary>

```{r}
sessionInfo()
```

</details>
